---
title: "Regression Models - Course Project"
author: "Necati Demir"
date: "02/20/2015"
output: html_document
---

###Prepare Data

```{r}
library(datasets)
library(ggplot2)
data(mtcars)

mtcars$am <- factor(mtcars$am, labels=c("Automatic", "Manual"))
```

###Is an automatic or manual transmission better for MPG?
Let's make a t test to understand if means of mpg variables for each transmission type are significantly different.

```{r}
ttest<-t.test(mpg~am, data=mtcars)
print(ttest)
```

According to t test, there is a significance difference of means of mpg variables for each tranmission type. Let's validate by plotting.

```{r}
plt<-ggplot(mtcars, aes(am, mpg, group=am,color=am)) + geom_boxplot()
print(plt)
```

###Quantify the MPG difference between automatic and manual transmissions

To understand which variables most effect the lm, we will use step function.

```{r}
stepmodel<-step(lm(mpg~., data=mtcars), trace=0)
print(stepmodel)
```

It seems that wt, qsec and am variables are the variables that effect the lm. We will train run lm again by using variables wt and qsec, controled by am.

```{r}
model<-lm(mpg~ am:(wt+qsec),data=mtcars)
print(model)
```

* Increasing weight for cars which have manual tranmission decreases the mpg more than increasing weight for cars which have automatic tranmission. Let's plot this.

```{r}
plt<-ggplot(mtcars, aes(wt, mpg, group=am,color=am)) + geom_line()
print(plt)
```


* Increasing qsec for cars which have manual tranmission increases the mpg more than increasing qsec for cars which have automatic tranmission. Let's plot this.

```{r}
plt<-ggplot(mtcars, aes(qsec, mpg, group=am,color=am)) + geom_line()
print(plt)
```