---
title: "Practical Machine Learning - Course Project"
author: "Necati Demir"
date: "02/19/2015"
output: html_document
---

###Include Libraries

We will use caret machine learning library. doMC library is used for concurrency.

```{r}
library(caret)
library(doMC)
registerDoMC(cores = 4)
```

###Reading Data

Data contains character values like NA and DIV/O!. We will read the dataset and make these values as NA.

```{r}
training<-read.csv("pml-training.csv", na.strings=c("NA","#DIV/0!",""))
predictDataset<-read.csv("pml-testing.csv", na.strings=c("NA","#DIV/0!",""))
```

###Cleaning Data

We will remove first five columns. These are

* "" -> used as id
* "user_name"
* "raw_timestamp_part_1"
* "raw_timestamp_part_2"
* "cvtd_timestamp"

```{r, echo=FALSE}
#remove first five columns
training<-training[,-c(1:5)]
```

The next step is to assign values to NAs. The mean of column values will be assigned to NAs.

```{r}
#calculate mean for each integer and numerics columns
#assigns means to NAs
for (colName in names(training)){
  
  if(class(training[[colName]]) %in% c("integer", "numeric")){
    m<-mean(training[[colName]], na.rm = TRUE)
    training[[colName]][is.na(training[[colName]])]<-m
  }
  
}
```

Now, let's remove the columns where variance is near zero.

```{r}
training<-training[,-nearZeroVar(training)]
```

###Splitting Dataset

```{r}
index <- createDataPartition(y=training$classe, p=0.6, list=FALSE)
trainingData <- training[index, ]
testingData <- training[-index, ]
```

###Training

We will do training by using Random Forest algorithm, 3 Cross Validation will be used.

```{r}
train_control <- trainControl(method="cv", number=3)
model <- train(classe~., data=trainingData, method="rf", trControl = train_control)
```

###Prediction 

First we will make predictions on training dataset and then on testing dataset. This will produce error rates.

```{r}
prediction <- predict(model, trainingData, type="raw")
c<-confusionMatrix(prediction, trainingData$classe)
print("In Sample Error Rate")
print(1-c[["overall"]][["Accuracy"]])

prediction <- predict(model, testingData, type="raw")
c<-confusionMatrix(prediction, testingData$classe)
print("Out of Sample Error Rate")
print(1-c[["overall"]][["Accuracy"]])
```

###Generate Data for Submitting

```{r}
#generate data for submitting
prediction <- predict(model, predictDataset, type="raw")

for (i in seq(20)){
  fileName<-paste("problem",i,".txt",sep="_")
  write.table(prediction[i],file=fileName,quote=FALSE,row.names=FALSE,col.names=FALSE)
}
```