---
title: "Statistical Inference - Course Project"
author: "Necati Demir"
date: "02/21/2015"
output: html_document
---

In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. Note that you will need to do a thousand simulations.

##Simulation

```{r}
lambda<-.2
nSample=40
nSimulation=1000
hist(rexp(1000, lambda))
data = NULL
for (i in 1 : nSimulation) data = c(data, mean(rexp(nSample, lambda)))
hist(data)
```

##Sample Mean versus Theoretical Mean

```{r}
sample_mean <- mean(data)
theory_mean <- 1/lambda
print(sample_mean)
print(theory_mean)
```

##Sample Variance versus Theoretical Variance

```{r}
sample_var <- var(data)
theory_sd <- (1/lambda)/sqrt(nSample)
theory_var<-theory_sd^2
print(sample_var)
print(theory_var)
```

##Distribution
How one can tell the distribution is approximately normal?

```{r}
library(ggplot2)
data<-data.frame(data)
g<-ggplot(data, aes(x=data))+geom_histogram(aes(y = ..density..))+stat_function(fun=dnorm,args=list( mean=mean(data$data), sd=sd(data$data)),color="blue")
print(g)
```